Automatic Matching of Bullet Lands

### 2017-06-22 imaging-paper.Rnw
first couple of figures - had to change path, will change back

\linenumbers
%\tableofcontents
%\newpage
<<setup, fig.keep='all', cache=FALSE, echo=FALSE, eval=TRUE, message=F, warning=F>>=
#rm(list=ls())
#wd <- getwd()
library(extrafont)
library(knitr)
imgdir <- "Figure/"
codedir <- "code"
datadir <- "images/Hamby (2009) Barrel/bullets"

@@

qplot(data=subset(dbr111, x <= 100*1.5625^2 & x >= 99*1.5625^2), y, value, geom="line", size=I(1)) +
  geom_line(aes(x=xpred, y=ypred, group=x), 
            colour="grey30", size=0.25) +
#  ylab(expression(paste("Surface Measurements (in ",mu,m,")", sep=""))) + 
  ylab("") +
  theme_bw() + 
  theme(legend.position="bottom") #+ coord_equal()
@
\caption{\label{fig:fixedX}Side profile of the surface measurements (in~$\mu m$) of a bullet land at a fixed height $x$. Note that the global features dominate any deviations, corresponding to the individual characteristics of striation marks.}
\end{figure}

@@

p1 <- qplot(y, value, data = br111_bullet, size=I(1)) + theme_bw() + ylab("Surface measurements")
p1
@
\end{subfigure}
\begin{subfigure}[t]{\textwidth}\centering
\caption{\label{fig:loess_step3}Step 2 of identifying shoulder locations: The  surface measurements are smoothed twice with a smoothing factor of $s = 35$. The orange rectangle shows an example of the smoothing window. Valleys and peaks are detected, if they are not within the same window.}
<<loess_step3, echo=FALSE, fig.width=10, fig.height=3.5, out.width='.5\\textwidth', warning=FALSE,  message=FALSE>>=
subdata <- br111_bullet
smoothfactor <- 35

@@

xloc=250
p3 <- ggplot() +
  annotate("rect",xmin=xloc-17*1.5625, xmax=xloc+18*1.5625, ymin=80, ymax=200, fill=alpha("orange", alpha=0.5)) + 
  geom_point(aes(x=(1:length(smoothed_truefalse))*1.5625, y=smoothed_truefalse)) + theme_bw() +
    geom_vline(xintercept=xloc, colour="grey50") + xlab("y") + ylab("Surface measurements")

@@

    p4 <- qplot(subdata$y[subdata$y < subdata$y[groove_ind]], subdata$value[subdata$y < subdata$y[groove_ind]], colour=I("grey60"), alpha=I(.25)) +
        ylim(c(min(subdata$value[!is.nan(subdata$value)]) - 25, max(subdata$value[!is.nan(subdata$value)]) + 25)) +
        xlim(c(min(subdata$y) - 25, max(subdata$y) + 25)) +
        geom_point(aes(x, y), data = data.frame(x = subdata$y[subdata$y > subdata$y[groove_ind2]], y = subdata$value[subdata$y > subdata$y[groove_ind2]]), colour=I("grey60"), alpha=I(.25)) +
        geom_point(inherit.aes = FALSE, aes(x, y), data = data.frame(x = subdata$y[subdata$y < subdata$y[groove_ind2] & subdata$y > subdata$y[groove_ind]], y = subdata$value[subdata$y < subdata$y[groove_ind2] & subdata$y > subdata$y[groove_ind]])) +
        theme_bw() +
        geom_vline(xintercept = subdata$y[peak_ind], colour = "red") +
        geom_vline(xintercept = subdata$y[groove_ind], colour = "blue") +
        geom_vline(xintercept = subdata$y[peak_ind2], colour = "red") +
        geom_vline(xintercept = subdata$y[groove_ind2], colour = "blue") +
      xlab("y") + ylab("Surface measurements")

@@

my.loess$fitted + ylab("Surface measurements")
@
\end{subfigure}
\begin{subfigure}[b]{.49\textwidth}\centering
\caption{\label{fig:loess_resid} Residuals of loess fit for bullet~1-5.
}
%<<loess_resid, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\textwidth', warning=FALSE>>=
%my.loess$resid + ylab("Residuals of loess Fit") 
%@
<<boot_loess, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\textwidth', warning=FALSE>>=
#boot.loess <- boot_fit_loess(br111_bullet, br111.groove)
#poly <- with(boot.loess, data.frame(x = c(y,rev(y)), y=c(high, rev(low))))
#qplot(x=x, y=y, geom="polygon", fill=I("steelblue"), data=poly) +
ggplot() +
  geom_line(aes(x=y, y=resid), data=my.loess$data) +
  ylab("Residuals of loess fit") + xlab("y") + theme_bw()
@
\end{subfigure}
\caption{Fit and residuals of a loess fit to bullet~1-5 (Barrel~1). The residuals define the {\it signature} of bullet~1-5. %Blue areas around the residuals show  95\% bootstrap confidence intervals (based on $B=1,000$ bootstrap samples).
}
\end{figure}
%

>>>>

\linenumbers
%\tableofcontents
%\newpage
<<setup, fig.keep='all', cache=FALSE, echo=FALSE, eval=TRUE, message=F, warning=F>>=
#rm(list=ls())
#wd <- getwd()
library(extrafont)
library(knitr)
imgdir <- "Figure/"
codedir <- "code"
datadir <- "/Users/heike/papers/dissertations/eric-dissertation/images/Hamby (2009) Barrel/bullets/"
#datadir <- "images/Hamby (2009) Barrel/bullets"

@@

qplot(data=subset(dbr111, x <= 100*1.5625^2 & x >= 99*1.5625^2), y, value, geom="line", size=I(1)) +
  geom_line(aes(x=xpred, y=ypred, group=x), 
            colour="grey30", size=0.25) +
  ylab(expression(paste("Relative Height (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
#  ylab("") +
  theme_bw() + 
  theme(legend.position="bottom") #+ coord_equal()
@
\caption{\label{fig:fixedX}Side profile of the surface measurements (in~$\mu m$) of a bullet land at a fixed height $x$. Note that the global features dominate any deviations, corresponding to the individual characteristics of striation marks.}
\end{figure}

@@

p1 <- qplot(y, value, data = br111_bullet, size=I(1)) + theme_bw() + 
    ylab(expression(paste("Relative Height (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  theme(text = element_text(size=20))

p1
@
\end{subfigure}
\begin{subfigure}[t]{\textwidth}\centering
\caption{\label{fig:loess_step3}Step 2 of identifying shoulder locations: The  surface measurements are smoothed twice with a smoothing factor of $s = 35$. The orange rectangle shows an example of the smoothing window. Valleys and peaks are detected, if they are not within the same window.}
<<loess_step3, echo=FALSE, fig.width=10, fig.height=3.5, out.width='.5\\textwidth', warning=FALSE,  message=FALSE>>=
subdata <- br111_bullet
smoothfactor <- 35

@@

xloc=250
p3 <- ggplot() +
  annotate("rect",xmin=xloc-17*1.5625, xmax=xloc+18*1.5625, ymin=80, ymax=200, fill=alpha("orange", alpha=0.5)) + 
  geom_point(aes(x=(1:length(smoothed_truefalse))*1.5625, y=smoothed_truefalse)) + theme_bw() +
    geom_vline(xintercept=xloc, colour="grey50") + 
    ylab(expression(paste("Relative Height (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  theme(text = element_text(size=20))

@@

    p4 <- qplot(subdata$y[subdata$y < subdata$y[groove_ind]], subdata$value[subdata$y < subdata$y[groove_ind]], colour=I("grey60"), alpha=I(.25)) +
        ylim(c(min(subdata$value[!is.nan(subdata$value)]) - 25, max(subdata$value[!is.nan(subdata$value)]) + 25)) +
        xlim(c(min(subdata$y) - 25, max(subdata$y) + 25)) +
        geom_point(aes(x, y), data = data.frame(x = subdata$y[subdata$y > subdata$y[groove_ind2]], y = subdata$value[subdata$y > subdata$y[groove_ind2]]), colour=I("grey60"), alpha=I(.25)) +
        geom_point(inherit.aes = FALSE, aes(x, y), data = data.frame(x = subdata$y[subdata$y < subdata$y[groove_ind2] & subdata$y > subdata$y[groove_ind]], y = subdata$value[subdata$y < subdata$y[groove_ind2] & subdata$y > subdata$y[groove_ind]])) +
        theme_bw() +
        geom_vline(xintercept = subdata$y[peak_ind], colour = "red") +
        geom_vline(xintercept = subdata$y[groove_ind], colour = "blue") +
        geom_vline(xintercept = subdata$y[peak_ind2], colour = "red") +
        geom_vline(xintercept = subdata$y[groove_ind2], colour = "blue") +
      ylab(expression(paste("Relative Height (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  theme(text = element_text(size=20))

@@

my.loess$fitted + ylab(expression(paste("Relative Height (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  theme(text = element_text(size=20))
@
\end{subfigure}
\begin{subfigure}[b]{.49\textwidth}\centering
\caption{\label{fig:loess_resid} Residuals of loess fit for bullet~1-5.
}
%<<loess_resid, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\textwidth', warning=FALSE>>=
%my.loess$resid + ylab("Residuals of loess Fit") 
%@
<<boot_loess, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\textwidth', warning=FALSE>>=
#boot.loess <- boot_fit_loess(br111_bullet, br111.groove)
#poly <- with(boot.loess, data.frame(x = c(y,rev(y)), y=c(high, rev(low))))
#qplot(x=x, y=y, geom="polygon", fill=I("steelblue"), data=poly) +
ggplot() +
  geom_line(aes(x=y, y=resid), data=my.loess$data) +
  theme_bw() +
  ylab(expression(paste("Residuals (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  theme(text = element_text(size=20))

@
\end{subfigure}
\caption{Fit and residuals of a loess fit to bullet~1-5 (Barrel~1). The residuals define the {\it signature} of bullet~1-5. %Blue areas around the residuals show  95\% bootstrap confidence intervals (based on $B=1,000$ bootstrap samples).
}
\end{figure}
%

### 2017-06-22 imaging-paper.tex
first couple of figures - had to change path, will change back

\subsection{Algorithm}\label{sec:algorithm}

\begin{figure}[hbtp]
\centering
    \begin{subfigure}[t]{\textwidth}\centering
\caption{Loess smooth of signatures  at a height of $x = 100\mu m$ (span is 0.03).\label{fig:smooth}}{%
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=.65\textwidth]{figure/smooth-1}

\end{knitrout}
    }
\end{subfigure}
\begin{subfigure}[t]{\textwidth}\centering
\caption{Using a rolling median peaks and valleys are identified for each signature. Peaks and valleys on the signature correspond to striation marks on the bullet's surface. \label{fig:smoothcutb}}{%
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=.65\textwidth]{figure/smoothcut-1}

\end{knitrout}
}
\end{subfigure}    
\begin{subfigure}[t]{\textwidth}\centering
    \caption{Rectangles in the back identify a striation mark on one of the bullets.  Matching striation marks are indicated by color filled rectangles and marked by an `o'. Mismatches are filled in grey and  marked by an `x'.   \label{fig:smoothcutd}}{%
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=.65\textwidth]{figure/smoothmatch-1}

\end{knitrout}
    }
\end{subfigure}
\caption{\label{fig:match}Matching striation marks: smooth (a), identify peaks and valley (b), and match peaks and valleys between signatures (c).}
\end{figure}
%\afterpage{\clearpage}
Figure~\ref{fig:match} gives an overview of the automated matching routine: 
We first identify a stable region for each bullet land and extract the signature at the lowest height in this region, because typically, individual characteristics are best expressed at the lower end of the bullet (see Supplement Section~\ref{supp:bulletbottom} for a more detailed discussion).

@@

\subsection{Horizontal alignment}
Signatures of each of the two lands, 1-5 and 2-1,  in Figure~\ref{fig:manualmatch-rgl} are shown in Figure~\ref{fig:cross100} extracted at a height of $x = 100\mu m$. Striation marks show up in these representations as peaks and valleys.  The individual characteristics are prominent and, again, suggest a match between the lands. A horizontal shift of one of the signatures (result shown in Fig~\ref{fig:crosscutX}) emphasizes the strong similarities between signatures. 
%
\begin{figure}[hbtp]
\centering
\begin{subfigure}[b]{.49\textwidth}\centering
\caption{Raw bullet land signatures.\label{fig:crosscut}}{%
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\textwidth]{figure/crosscuts-1}

\end{knitrout}
    }
\end{subfigure}    
\begin{subfigure}[b]{.49\textwidth}\centering
    \caption{Aligned signatures.\label{fig:crosscutX}}{%
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\textwidth]{figure/crosscutsX-1}

\end{knitrout}
    }
\end{subfigure}
\caption{\label{fig:cross100}Signatures of bullets 1-5 and 2-1 taken at  heights of $x = 100\mu m$. A horizontal shift of the values of bullet~1-5 to the right shows the similarity of the striation marks.}
\end{figure}
%
For this alignment we use the cross-correlation function to find a maximal amount of agreement between the signatures \citep{bachrach:2002, chu:2010, vorburger:2011, thompson:2013}.
This horizontal shift is based on the cross-correlation between the two signatures: let $f(t)$ and $g(t)$ define the signature values  at $t$, where $t$ are locations between 0~$\mu m$ and about 2500~$\mu m$, 1.5625~$\mu m$ apart.
The cross-correlation between $f$ and $g$ at lag $k$ is then defined as
\[
(f * g) (k) = \sum_t f(t+k) g(t),
\]
with suitably defined limits for the summation. % (because variances of $f$ and $g$ do not change, the above equation is proportional to the correlation).

\begin{figure}[hbtp]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=.65\textwidth]{figure/ccf-1}

>>>>

\subsection{Algorithm}\label{sec:algorithm}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning in unzip(path, exdir = mydir): error 1 in extracting from zip file}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: 'NA' does not exist in current working directory ('/Users/heike/papers/2015-imaging-paper').}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning in unzip(path, exdir = mydir): error 1 in extracting from zip file}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: 'NA' does not exist in current working directory ('/Users/heike/papers/2015-imaging-paper').}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in data.frame(subLOFx1): object 'subLOFx1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'lofX' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'lofX' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in factor(lofX\$r05): object 'lofX' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in levels(lofX\$type) <- c("{}groove"{}, NA, "{}peak"{}): object 'lofX' not found}}\end{kframe}
\end{knitrout}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning in unzip(path, exdir = mydir): error 1 in extracting from zip file}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: 'NA' does not exist in current working directory ('/Users/heike/papers/2015-imaging-paper').}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning in unzip(path, exdir = mydir): error 1 in extracting from zip file}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: 'NA' does not exist in current working directory ('/Users/heike/papers/2015-imaging-paper').}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'subLOFx1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'subLOFx2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in ccf(subLOFx1\$resid, subLOFx2\$resid, lag.max = 100, plot = FALSE): object 'subLOFx1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in ccf\$lag: object of type 'closure' is not subsettable}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'subLOFx1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in data.frame(subLOFx1): object 'subLOFx1' not found}}\end{kframe}
\end{knitrout}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'lofX' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in matches\$allnas: object of type 'closure' is not subsettable}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in matches\$allnas: object of type 'closure' is not subsettable}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}group\_by\_"{}): no applicable method for 'group\_by\_' applied to an object of class "{}function"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in subset.default(lines, lineid != 0): object 'lineid' not found}}\end{kframe}
\end{knitrout}

\begin{figure}[hbtp]
\centering
    \begin{subfigure}[t]{\textwidth}\centering
\caption{Loess smooth of signatures  at a height of $x = 100\mu m$ (span is 0.03).\label{fig:smooth}}{%
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in strsplit(as.character(x), split = "{}/"{}): object 'lofX' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in ggplot(data, aesthetics, environment = env): object 'lofX' not found}}\end{kframe}
\end{knitrout}
    }
\end{subfigure}
\begin{subfigure}[t]{\textwidth}\centering
\caption{Using a rolling median peaks and valleys are identified for each signature. Peaks and valleys on the signature correspond to striation marks on the bullet's surface. \label{fig:smoothcutb}}{%
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: 'NA' does not exist in current working directory ('/Users/heike/papers/2015-imaging-paper').}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: 'NA' does not exist in current working directory ('/Users/heike/papers/2015-imaging-paper').}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in rbind(subLOFx1, subLOFx2): object 'subLOFx1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'lof' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in unique(data\$bullet): object 'lof' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'bAlign' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in unique(lof\$bullet): object 'lof' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in subset(lofX, bullet == b12[1]): object 'lofX' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in subset(lofX, bullet == b12[2]): object 'lofX' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'b12' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'b12' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in rbind(peaks1\$lines, peaks2\$lines): object 'peaks1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in strsplit(as.character(x), split = "{}/"{}): object 'peaks' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in strsplit(as.character(x), split = "{}/"{}): object 'lofX' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in fortify(data): object 'peaks' not found}}\end{kframe}
\end{knitrout}
}
\end{subfigure}    
\begin{subfigure}[t]{\textwidth}\centering
    \caption{Rectangles in the back identify a striation mark on one of the bullets.  Matching striation marks are indicated by color filled rectangles and marked by an `o'. Mismatches are filled in grey and  marked by an `x'.   \label{fig:smoothcutd}}{%
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'b12' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'b12' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in rbind(lines1, lines2): object 'peaks1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in !match: invalid argument type}}\end{kframe}
\end{knitrout}
    }
\end{subfigure}
\caption{\label{fig:match}Matching striation marks: smooth (a), identify peaks and valley (b), and match peaks and valleys between signatures (c).}
\end{figure}
%\afterpage{\clearpage}
Figure~\ref{fig:match} gives an overview of the automated matching routine: 
We first identify a stable region for each bullet land and extract the signature at the lowest height in this region, because typically, individual characteristics are best expressed at the lower end of the bullet (see Supplement Section~\ref{supp:bulletbottom} for a more detailed discussion).

@@

\subsection{Horizontal alignment}
Signatures of each of the two lands, 1-5 and 2-1,  in Figure~\ref{fig:manualmatch-rgl} are shown in Figure~\ref{fig:cross100} extracted at a height of $x = 100\mu m$. Striation marks show up in these representations as peaks and valleys.  The individual characteristics are prominent and, again, suggest a match between the lands. A horizontal shift of one of the signatures (result shown in Fig~\ref{fig:crosscutX}) emphasizes the strong similarities between signatures. 
%
\begin{figure}[hbtp]
\centering
\begin{subfigure}[b]{.49\textwidth}\centering
\caption{Raw bullet land signatures.\label{fig:crosscut}}{%
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in strsplit(as.character(x), split = "{}/"{}): object 'lof' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in ggplot(data, aesthetics, environment = env): object 'lof' not found}}\end{kframe}
\end{knitrout}
    }
\end{subfigure}    
\begin{subfigure}[b]{.49\textwidth}\centering
    \caption{Aligned signatures.\label{fig:crosscutX}}{%
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in strsplit(as.character(x), split = "{}/"{}): object 'lofY' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in ggplot(data, aesthetics, environment = env): object 'lofY' not found}}\end{kframe}
\end{knitrout}
    }
\end{subfigure}
\caption{\label{fig:cross100}Signatures of bullets 1-5 and 2-1 taken at  heights of $x = 100\mu m$. A horizontal shift of the values of bullet~1-5 to the right shows the similarity of the striation marks.}
\end{figure}
%
For this alignment we use the cross-correlation function to find a maximal amount of agreement between the signatures \citep{bachrach:2002, chu:2010, vorburger:2011, thompson:2013}.
This horizontal shift is based on the cross-correlation between the two signatures: let $f(t)$ and $g(t)$ define the signature values  at $t$, where $t$ are locations between 0~$\mu m$ and about 2500~$\mu m$, 1.5625~$\mu m$ apart.
The cross-correlation between $f$ and $g$ at lag $k$ is then defined as
\[
(f * g) (k) = \sum_t f(t+k) g(t),
\]
with suitably defined limits for the summation. % (because variances of $f$ and $g$ do not change, the above equation is proportional to the correlation).

\begin{figure}[hbtp]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in ccf\$lag: object of type 'closure' is not subsettable}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in ccf\$lag: object of type 'closure' is not subsettable}}\end{kframe}
\includegraphics[width=.65\textwidth]{figure/ccf-1}
